|

### 2020-02-04 analysis/paper/paper.Rmd
reduce overlap in figure labels, more iterations, clarify assumptions

Here, we show how visual encounter data can improve abundance estimates in capture-recapture studies for study designs where 1) individual identification requires capture (so that a subset of encountered individuals are captured), and 2) individuals can be encountered at most once per sampling occasion. 
We develop a modified capture-recapture observation model, and investigate conditions under which encounter data improve abundance estimates.
The methods presented here accommodate both failed captures and counts of animals collected separately from capture-recapture surveys, and can be integrated with existing capture-recapture models.

@@

Draws from the posterior distributions of all models were simulated using JAGS, with six parallel Markov chain Monte Carlo chains, and 300,000 iterations per chain with an adaptation period of 30,000, a burn-in period of 100,000, and posterior thinning by 300 to reduce memory usage [@plummer2003jags]. 
Convergence was assessed using visual inspection of traceplots, and the potential scale reduction factor ($\hat{R}$) statistic [@gelman1992inference].
All code to replicate the analyses is available in a research compendium at [https://github.com/mbjoseph/secmr](https://github.com/mbjoseph/secmr).

>>>>

Here, we show how visual encounter data can improve abundance estimates in capture-recapture studies for study designs where 1) individual identification requires capture, 2) a subset of encountered individuals are captured, and 3) individuals can be encountered at most once per sampling occasion. 
We develop a modified capture-recapture observation model, and investigate conditions under which encounter data improve abundance estimates.
The methods presented here accommodate both failed captures and counts of animals collected separately from capture-recapture surveys, and can be integrated with existing capture-recapture models.

@@

Draws from the posterior distributions of all models were simulated using JAGS, with six parallel Markov chain Monte Carlo chains, and 400,000 iterations per chain with an adaptation period of 200,000, a burn-in period of 40,000, and posterior thinning by 400 to reduce memory usage [@plummer2003jags]. 
Convergence was assessed using visual inspection of traceplots, and the potential scale reduction factor ($\hat{R}$) statistic [@gelman1992inference].
All code to replicate the analyses is available in a research compendium at [https://github.com/mbjoseph/secmr](https://github.com/mbjoseph/secmr).
